\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-21 trunk/intro.tex
Activated section numbering

This chapter is organized as follows. We start with some foundational
concepts in our Planning framework in Section
\ref{sec:concepts}. \comment{add others} We conclude with Section
\ref{sec:conclusion}.

>>>>

This chapter is organized as follows. We start with some foundational
concepts in our Planning framework in Section~\ref{sec:concepts} which
includes a brief overview of AI Planning in
Section~\ref{sec:planningfound}. In Section~\ref{sec:basics} we go
deeper into the \eu framework itself, the basis of all deliberation
within \rx. A key portion is Section~\ref{sec:europa:pr} which details
the Internal plan representation essential to planning within a
situated agent like \rx. Modeling (Section~\ref{sec:europa:modeling}),
Inference (Section~\ref{sec:europa:inference}) and Search
(Section~\ref{sec:europa:search}) further detail the important details
associated with \eu for the reader. With these foundational elements
out of the way, we transition to \rx in Section~\ref{sec:arch}, bring
out architectural details in Section~\ref{sec:arch:trex}, deal with
the execution cycle in Section~\ref{sec:arch:exec}, highlight how \rx
deliberates in Section~\ref{sec:arch:europa} finally delving deeper
into the key concept of synchronization in
Section~\ref{sec:arch:synch}. Further details on deliberation within
\rx (Section~\ref{sec:arch:plan}) and how planning and execution are
interleaved are shown in Section~\ref{sec:arch:intertwine}. We offer
results from our experiments at sea in Section~\ref{sec:results},
offer some insights into the near-term future goals of our research in
Section~\ref{sec:future} and conclude with
Section~\ref{sec:conclusion}.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "setobook"
%%% End:
